InteroceptionScale (study 2) - Data Analysis

### 2025-02-05 study2/analysis/1_cleaning.qmd
update cleaning

```{r}
# Compute distance
dfoutlier <- performance::check_outliers(select(df, contains("MINT_")), 
                                         method=c("optics"),
                                         threshold=list(optics=2.5, optics_xi=0.03)) |> 
  as.data.frame() |> 
  mutate(Participant = fct_reorder(df$Participant, Distance_OPTICS),
         Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
         Outlier_Duration = ifelse(Participant %in% outliers$duration, 1, 0),
         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Checks", "Passed"),
         Outlier = ifelse(Outlier == "Passed" & Outlier_Duration == 1, "Duration", Outlier))

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 8, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

p1 <- dfoutlier |> 
  ggplot(aes(x=Participant, y=Distance_OPTICS)) +
  geom_bar(aes(fill=Outlier), stat="identity") +
  geom_hline(yintercept = 8, linetype="dashed", color="red") +
  labs(fill = "Status") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        panel.grid.major.x = element_blank())

@@

p2 <- estimate_relation(m, length=30) |> 
  ggplot(aes(x=Distance_OPTICS, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  geom_vline(xintercept=8, linetype="dashed", color="red") +
  theme_minimal()

@@

@@

p_edu <- df |>
  mutate (Student = ifelse(is.na(Student), FALSE, Student)) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Student)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

@@

### Country of Residence

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```

@@

### Mental Health

>>>>

```{r}
# Compute distance
dfoutlier <- performance::check_outliers(select(df, contains("MAIA_")), 
                                         method=c("optics"),
                                         threshold=list(optics=2.5, optics_xi=0.03)) |> 
  as.data.frame() |> 
  mutate(Participant = fct_reorder(df$Participant, Distance_OPTICS),
         Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
         Outlier_Duration = ifelse(Participant %in% outliers$duration, 1, 0),
         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Checks", "Passed"),
         Outlier = ifelse(Outlier == "Passed" & Outlier_Duration == 1, "Duration", Outlier))

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 4, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

p1 <- dfoutlier |> 
  ggplot(aes(x=Participant, y=Distance_OPTICS)) +
  geom_bar(aes(fill=Outlier), stat="identity") +
  geom_hline(yintercept = 4, linetype="dashed", color="red") +
  labs(fill = "Status") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        panel.grid.major.x = element_blank())

@@

p2 <- estimate_relation(m, length=30) |> 
  ggplot(aes(x=Distance_OPTICS, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  geom_vline(xintercept=4, linetype="dashed", color="red") +
  theme_minimal()

@@

## Imputation

```{r}
#| eval: FALSE

set.seed(3)

d <- datawizard::data_partition(df, proportion = 0.8)

m1 <- glm(MINT_InteroceptiveFailures_10 ~ .,
          family = poisson(),
          data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))

m2 <- parsnip::rand_forest("regression", mtry = 10, trees = 2000) |> 
  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))

m3 <- parsnip::mlp(mode="regression") |> 
  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))

# m4 <- parsnip::bart(mode="regression") |> 
#   fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))

library(baguette)

m5 <- parsnip::bag_mlp(mode="regression") |>
  fit(MINT_InteroceptiveFailures_10 ~ ., data = select(d$p_0.8, starts_with("MINT_"), -contains("AttentionCheck")))

# glmmTMB::glmmTMB(MINT_InteroceptiveFailures_10 ~ .,
#                  family = poisson(),
#                  ziformula=~1,
#                  data = select(df, starts_with("MINT_"), -contains("AttentionCheck")))

parsnip::glance(m5)
parsnip::tidy(m5)

results <- data.frame(
  TrueScore = d$test$MINT_InteroceptiveFailures_10,
  # Poisson = predict(m1, d$test),
  RandomForest = predict(m2, d$test)$.pred,
  MLP = predict(m3, d$test)$.pred,
  BagMLP = predict(m5, d$test)$.pred
) |> 
  pivot_longer(-TrueScore)

results |> 
  ggplot(aes(x=TrueScore, y=value, color=name)) +
  geom_abline(slope=1) +
  geom_point()

# Compute R^2
SS_res <- sum((df$TrueScore - df$PredictedScore)^2)
SS_tot <- sum((df$TrueScore - mean(df$TrueScore))^2)
R2 <- 1 - (SS_res / SS_tot)

results |> 
  summarize(RMSE = sqrt(mean((TrueScore - value)^2)),
            SS_res = sum((TrueScore - value)^2),
            SS_tot = sum((TrueScore - mean(value))^2),
            R2 = 1 - (SS_res / SS_tot),
            .by="name")

# Compute R2

```

@@

p_edu <- df |>
  mutate(Student = ifelse(is.na(Student), FALSE, Student),
         Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Student)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

@@

### Country

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |>
  rename(Country = Var1) |> 
  arrange(desc(Freq)) |> 
  gt::gt()
```

@@

### Health

### 2025-02-05 study2/analysis/2_analysis.qmd
update cleaning

  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",

@@

  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
  MINT_AttentionCheck_1 = "I can always accurately answer to the extreme left on this question to show that I am reading it")

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

>>>>

  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"

@@

  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"
)

@@

ega1 <- bootEGA(
  items,
  na.data = "pairwise",
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)
